Argennon: A Scalable Smart Contract Platform

### 2021-06-08 tex/sections/avm.tex
Fix a few typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In the Argennon Virtual Machine four distinct identifier values exist: \texttt{applicationID}, \texttt{accountID},
\texttt{methodID} and \texttt{chunkID}.

@@

As we explained in Section~\ref{subsec:method-invocation} by using \texttt{invoke\_internal} instruction, a smart
contract can invoke methods of another smart contract in its own context. This is how AVM smart contracts
invoke methods of the AVM standard library. Methods of the AVM standard library are stored
with the \texttt{applicationID} zero in the AVM method area. This implies that the AVM standard library is actually
a part of the root smart contract.

>>>>

In the Argennon Virtual Machine four distinct identifier types exist: \texttt{applicationID}, \texttt{accountID},
\texttt{methodID} and \texttt{chunkID}.

@@

As we explained in Section~\ref{subsec:method-invocation} by using \texttt{invoke\_internal} instruction, a smart
contract can invoke methods of another smart contract in its own context. AVM smart contracts use this instruction to
invoke methods of the AVM standard library. Methods of the AVM standard library are stored
with the \texttt{applicationID} zero in the AVM method area. This implies that the AVM standard library is actually
a part of the root smart contract.

### 2021-06-08 tex/sections/persistence.tex
Fix a few typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
method byte codes\footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, methods and chunks, can be considered as continuous pieces of byte addressable memory
which we shall call \emph{objects} throughout this chapter.

@@

Every block of the Argennon blockchain contains a set of \emph{clustering directives}. These directives
can only modify pages that were used for validating the block, and can
include directives for moving an object from one page to another or directives specifying which pages will contain
the newly created objects. These directives will always be run by nodes at the end of block validation.

A block proposer usually obtains clustering directives from a third party source who enjoys a considerable amount of
computational power.\footnote{we can say the AVM clustering algorithm is essentially off-chain.} This federated approach
does not affect Argennon security, because the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not change the performance much.

>>>>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
method byte codes\footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, methods and chunks, can be considered as continuous pieces of byte addressable memory. Throughout this
chapter, we shall call these data elements \emph{objects}.

@@

Every block of the Argennon blockchain contains a set of \emph{clustering directives}. These directives
can only modify pages that were used for validating the block, and can
include directives for moving an object from one page to another or directives specifying which pages will contain
the newly created objects. These directives are always executed by nodes at the end of block validation.

A block proposer usually obtains clustering directives from a third party source that enjoys a considerable amount of
computational power.\footnote{we can say the AVM clustering algorithm is essentially off-chain.} This federated approach
does not affect Argennon security, because the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not change the performance much.
